Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-02-18 Paper/paper.tex
minor text changes

	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for blind players.

	There are still many games which were not developed in a way that everyone can play it.
	This paper aims to help to find a way to help the development of games as well as exploring existing accessibly features and ways to enhance them. 
	By looking at what TLOU2 did and thinking about what else could be done, we can work towards making games a better experience for everyone.

>>>>

	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.

	However, there are still many games which were not developed in a way that everyone can play it.
	With focus on blind players, this paper aims to find a way to help the development cycle of games as well as exploring existing accessibly features and ways to enhance them.
